Efficient static analysis of Marlowe contracts

### 2020-05-04 papers/static_analysis2020/paper.tex
Fix typo
Address reviews by @shmish111

In this section, we explain the techniques that we mentioned in Section~\ref{sec:Introduction}
more in detail, and we illustrate those techniques with examples from
the static analysis implementation of Marlowe.

@@

Some of the modifications that we can apply to a static analysis implementation
are localised, and they do not fundamentally affect the overall structure
of the implementation. This means that the implementation can remain
intuitive and close to the original semantics and model that we are
trying to analyze, as well as making sure that the changes introduce
fewer errors than a more serious restructure.

@@

As it turns out, we do not need to implement the semantics of the
\texttt{Close} construct at all, because it is impossible for the
\texttt{Close} construct to produce a failed payment: it only pays
whatever there is available. So we can safely remove it from the analysis.

@@

Of course, if the minimum slot number of the transaction is greater
or equal than the slot number in the timeout, then the first transaction
will execute past the \texttt{When} and into the timeout branch, and
we will not need the second transaction. In the same way, if we include
an input that is allowed by the \texttt{When} into the first transaction,
then the first transaction will continue into the corresponding \texttt{When}
branch, and we will not need the second transaction.

@@

One subtle detail that we realised during testing is that, even though
the diagram above shows that a \texttt{When} belongs to the next transaction,
because it will still be there after the previous transaction is executed,
the observations in the \texttt{Notify} cases will correspond to the
\texttt{State} before the \texttt{When} is executed, but to the slot
interfal of the transactions that triggers the \texttt{When}. The same
is true for \texttt{Value}s in the \texttt{Deposit} cases, since the amount
to deposit must be calculated without considering the effects of the
deposit itself.

@@

Errors often occur when optimising or translating. If the static analysis
implementation is close to the actual implementation, it is much less
likely that a mistake will be made when writing it. On the other hand,
if we have to craft a static analysis implementation that is equivalent
(in some sense) to the original, but is written in a very different
way, it is quite likely that we will make assumptions which do not
hold.

>>>>

In this section, we explain the techniques that we mentioned in Section~\ref{sec:Introduction}
in more detail, and we illustrate those techniques with examples from
the static analysis implementation of Marlowe.

@@

Some of the modifications that we can apply to a static analysis implementation
are localised, and they do not fundamentally affect the overall structure
of the implementation. This means that the implementation can remain
intuitive and close to the original semantics and model that we are
trying to analyze, as well as making changes less likely to introduce
errors than a more serious restructure.

@@

As it turns out, we do not need to implement the semantics of the
\texttt{Close} construct at all, because it is impossible for the
\texttt{Close} construct to produce a failed payment
(we have also proven this using Isabelle\footnote{\url{https://github.com/input-output-hk/marlowe/blob/master/isabelle/CloseSafe.thy}
(last visited on 04/04/2020)}): it only pays whatever there is available.
So we can safely remove it from the analysis.

@@

On the other hand, if the minimum slot number of the transaction is greater
or equal than the slot number in the timeout, then the first transaction
will execute past the \texttt{When} and into the timeout branch, and
we will not need the second transaction. In the same way, if we include
an input that is allowed by the \texttt{When} into the first transaction,
then the first transaction will continue into the corresponding \texttt{When}
branch, and we will not need the second transaction.

@@

One subtle detail that we realised during testing is that, even though
the diagram above shows that a \texttt{When} belongs to the next transaction,
because it will still be there after the previous transaction is executed,
the observations in the \texttt{Notify} cases will correspond to the
\texttt{State} before the \texttt{When} is executed, but to the slot
interval of the transactions that triggers the \texttt{When}. The same
is true for \texttt{Value}s in the \texttt{Deposit} cases, since the amount
to deposit must be calculated without considering the effects of the
deposit itself.

@@

Errors often occur when optimising or translating. If the static analysis
implementation is close to the actual implementation, it is much less
likely that a mistake will be made when writing it. On the other hand,
if we have to craft a static analysis implementation that is equivalent
(in some sense) to the original, but is written in a very different
way, it is more likely that we will make assumptions which do not
hold.
